Lang-gen model simulations

### 2018-10-11 analysis/model-simulations.Rmd
add elephants model

>>>>

## Elephants live in africa and asia

```{r}
elephants <- '
var probability = function(Dist, x) {
  return Math.exp(Dist.score(x));
}

var bins = [
  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
];

var theta = 1;
var params75 = {a:45, b: 15};
var params50 = {a:30, b: 30};
var params25 = {a:15, b: 45};
var params100 = {a:50, b: 1};

var allComponents = [params25, params50, params75, params100]
var nullParams = {a:1,b:2000};

var makeComponent = function(params){
  return Categorical({
  vs: bins,
  ps: map(function(b) {
    probability(Beta(params), b) + Number.EPSILON
  }, bins )
})
}

var statePrior = Infer({model: function(){
  var mainPlace = categorical({
    ps:[1, 1, 1, 1],
    vs:[
      {asia: true, africa: false}, {asia: false, africa: true},
      {asia: false, africa: false}, {asia: true, africa: true}
    ]
  });
  return {
    asia: sample(makeComponent(mainPlace.asia ? uniformDraw(allComponents) : nullParams)),
    africa: sample(makeComponent(mainPlace.africa ? uniformDraw(allComponents) : nullParams))
  }
}})

var thetaPrior = Infer({model: function(){
  return {
    asia: uniformDraw(
      [0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
       0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95]
    ),
    africa: uniformDraw(
      [0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
       0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95]
    )
  }
}});

var meaning = function(utt, state, theta) {
  state[utt] > theta[utt]
}

var listener0 = function(utterance, worldPriors, thresholdPriors) {
  Infer({model: function(){
    var state = sample(worldPriors)
    var theta = sample(thresholdPriors)
    var m = meaning(utterance, state, theta)
    condition(m)
    condition(state.africa + state.asia <= 1)
    return {state, theta}
  }})
}

var elephantsLiveInAsia = listener0("asia", statePrior, thetaPrior);
var asiaStatePosterior = marginalize(elephantsLiveInAsia,"state");
var asiaThresholdPosterior =  marginalize(elephantsLiveInAsia, "theta");

var elephantsLiveinAfricaAndAsia = listener0("africa", asiaStatePosterior, asiaThresholdPosterior)

var AfricaAndAsiaStatePosterior = marginalize(elephantsLiveinAfricaAndAsia, "state");

var AfricaAndAsiaThresholdPosterior =  marginalize(elephantsLiveinAfricaAndAsia, "theta");

var x = {asiaStatePosterior, AfricaAndAsiaStatePosterior}
x
'
```

```{r}
rs.eleph <- webppl(elephants)

rs.asia <- as.data.frame(rs.eleph$asiaStatePosterior)
rs.asiaafrica <- as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior)

rs.asia.marignals <- bind_rows(
  rs.asia %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.asia %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)

ggplot(rs.asia.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)
```
```{r}
rs.asiaafrica.marignals <- bind_rows(
  rs.asiaafrica %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.asiaafrica %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)

ggplot(rs.asiaafrica.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)
```
